\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}

\usepackage[round]{natbib}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage{caption}
\usepackage{fullpage}

\hypersetup{ bookmarks=true,     % show bookmarks bar?
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
                        % linkbordercolor)
citecolor=blue,      % color of links to bibliography
filecolor=magenta,  % color of file links
urlcolor=cyan          % color of external links
}

\usepackage{array}

\externaldocument{../../SRS/SRS}

\input{../../Comments}
\input{../../Common}

\begin{document}

\title{Module Interface Specification for \progname{}}

\author{\authname}

\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X} \toprule {\bf Date} & {\bf Version}
& {\bf Notes}\\
\midrule
Mar 17, 2025 & 1.0 & Creation\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

See SRS Documentation at
\url{https://github.com/Lychee-acaca/CAS741/blob/main/docs/SRS/SRS.pdf}.

\wss{Also add any additional symbols, abbreviations or acronyms}

\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}

\section{Introduction}

The following document details the Module Interface Specifications for
\progname.

This project focuses on reimplementing the Pan-Tompkins algorithm for R-wave
detection in ECG signal processing.

Complementary documents include the System Requirement Specifications and Module
Guide.  The full documentation and implementation can be found at
\url{https://github.com/Lychee-acaca/CAS741}.

\section{Notation}

\wss{You should describe your notation.  You can use what is below as a starting
  point.}

The structure of the MIS for modules comes from \citet{HoffmanAndStrooper1995},
with the addition that template modules have been adapted from
\cite{GhezziEtAl2003}.  The mathematical notation comes from Chapter 3 of
\citet{HoffmanAndStrooper1995}.  For instance, the symbol := is used for a
multiple assignment statement and conditional rules follow the form $(c_1
\Rightarrow r_1 | c_2 \Rightarrow r_2 | ... | c_n \Rightarrow r_n )$.

The following table summarizes the primitive data types used by \progname. 

\begin{center}
\renewcommand{\arraystretch}{1.2}
\noindent 
\begin{tabular}{l l p{7.5cm}} 
\toprule 
\textbf{Data Type} & \textbf{Notation} & \textbf{Description}\\ 
\midrule
character & $\text{char}$ & a single symbol or digit\\
integer & $\mathbb{Z}$ & a number without a fractional component in (-$\infty$,
$\infty$) \\
natural number & $\mathbb{N}$ & a number without a fractional component in [1,
$\infty$) \\
real & $\mathbb{R}$ & any number in (-$\infty$, $\infty$)\\
string & $\text{string}$ & -\\
\bottomrule
\end{tabular} 
\end{center}

\noindent
The specification of \progname \ uses some derived data types: sequences,
strings, and tuples. Sequences are lists filled with elements of the same data
type. Strings are sequences of characters. Tuples contain a list of values,
potentially of different types. In addition, \progname \ uses functions, which
are defined by the data types of their inputs and outputs. Local functions are
described by giving their type signature followed by their specification.

\section{Module Decomposition}

The following table is taken directly from the Module Guide document for this
project.

\begin{table}[h!]
\centering
\begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Level 1} & \textbf{Level 2}\\
\midrule

{Hardware-Hiding Module} & ~ \\
\midrule

\multirow{5}{0.3\textwidth}{Behaviour-Hiding Module}
& General Digital Filter Module \\
& Specified IIR Filter Module \\
& Math Module \\
& Pan Tompkins Algorithm Module \\
& Annotated Data RMSE Module \\
\midrule

\multirow{4}{0.3\textwidth}{Software Decision Module}
& Rwave Detect Module \\
& Input Output Processing Module \\
& Error Handler Module \\
& Logger Module \\
\bottomrule

\end{tabular}
\caption{Module Hierarchy}
\label{TblMH}
\end{table}

\newpage
~\newpage

\section{MIS of Hardware-Hiding Module} \label{MIS_HH}

This section outlines the formal specification of the Hardware-Hiding Module,
which provides an abstraction layer for interacting with hardware devices.

\subsection{Module}

Hardware-Hiding

\subsection{Uses}

None

\subsection{Syntax}

This section describes the syntax used in the Hardware-Hiding Module, including
the constants, programs, and routines that can be accessed.

\subsubsection{Exported Constants}

None

\subsubsection{Exported Access Programs}

\begin{center}
\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
\hline
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\hline
open & $\text{char}^n$, $\mathbb{N}$, $\mathbb{N}$ & $\mathbb{Z}$ & - \\
write & $\mathbb{Z}$, $\mathbb{N}^n$, $\mathbb{N}$ & $\mathbb{N}$ & - \\
read & $\mathbb{Z}$, $\mathbb{N}^n$, $\mathbb{N}$ & $\mathbb{N}$ & - \\
\hline
\end{tabular}
\end{center}

\subsection{Semantics}

This section provides the detailed functionality and behavior of the module’s
functions.

\subsubsection{State Variables}

This module does not maintain state variables.

\subsubsection{Environment Variables}

This module interacts with hardware devices, such as file systems or external
I/O devices.

\subsubsection{Assumptions}

\begin{itemize}
\item The input parameters to open must be valid and correspond to existing
hardware components.
\item The write operation assumes that the hardware device is available and
writable.
\item The read operation assumes that the hardware device is readable.
\end{itemize}

\subsubsection{Access Routine Semantics}

\noindent open(pathname, flags, mode):

See \url{https://en.wikipedia.org/wiki/Open_(system_call)}.

\noindent write(fd, buf, count):

See \url{https://en.wikipedia.org/wiki/Write_(system_call)}.

\noindent read(fd, buf, count):

See \url{https://en.wikipedia.org/wiki/Read_(system_call)}.

\subsubsection{Local Functions}

None

\newpage

\section{MIS of General Digital Filter Module} \label{MIS_GDF}

\subsection{Module}

General Digital Filter

\subsection{Uses}

None

\subsection{Syntax}

This section describes the syntax used in the General Digital Filter Module,
including the constants, programs, and routines that can be accessed.

\subsubsection{Exported Constants}

None

\subsubsection{Exported Access Programs}

\begin{center}
\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
\hline
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\hline
lfilter & $\mathbb{R}^n$, $\mathbb{R}^m$, $\mathbb{R}^t$ & $\mathbb{R}^t$ & - \\
\hline
\end{tabular}
\end{center}

\subsection{Semantics}

This section provides the detailed functionality and behavior of the module’s
functions.

\subsubsection{State Variables}

None

\subsubsection{Environment Variables}

None

\subsubsection{Assumptions}

\begin{itemize}
\item a1
\end{itemize}

\subsubsection{Access Routine Semantics}

\noindent lfilter(b, a, x):
\begin{itemize}
\item Calculate the filtered result of the sequence $x$ based on the given
filter parameters $b$ and $a$.
\item output: The result of the sequence $x$ after being filtered.
\end{itemize}

\subsubsection{Local Functions}

None

\newpage

\bibliographystyle {plainnat}
\bibliography {../../../refs/References}

\newpage

\section{Appendix} \label{Appendix}

\wss{Extra information if required}

\end{document}